---
output: html_document
editor_options: 
  chunk_output_type: console
---
title: "Sym_temp"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load Libraries 
```{r}
library(devtools)   # install.packages("devtools")
library(steponeR) # install_github("jrcunning/steponeR")
library(tidyverse) # install.packages("tidyverse")
library(cowplot) #install.packages("cowplot)
library(grid) #install.packages(grid)
```


#Importing raw qPCR data from Quant Studio Design and Analysis Software 
```{r}
# List Mermaid Reef and Sandy Cay Reef Symbiodiniaceae data files
plates <- list.files(path = "Data/qPCR", pattern = ".txt", full.names = TRUE)
plates
# Read in data and calculate target ratios
df <- steponeR(files = plates, 
               delim = "\t", 
               target.ratios = c("C.Orb", "D.Orb", "A.Orb", "B.Orb"), 
               fluor.norm = list(C = 2.234, D = 1, Orb = 1, A = 1, B = 1),
               copy.number = list(C = 20, D = 3, Orb = 1, A = 1, B = 1),
               ploidy = list(C = 1, D = 1, Orb = 2, A = 1, B = 1),
               extract = list(C = 0.813, D = 0.813, Orb = 0.982, A = 0.813, B = 0.813))
qpcr <- df$result

# View data
head(qpcr)
```


#Organizing Raw qPCR Data 
```{r}
# Change NA Orb values to 27 
qpcr <- qpcr %>% 
  mutate(Orb.CT.mean = ifelse(is.na(Orb.CT.mean), 27, Orb.CT.mean))

# Samples that did not amplify for any Symbiodiniaceae ("fails")
fails <- qpcr %>%
  filter(is.na(C.Orb) & is.na(D.Orb) & is.na(A.Orb) & is.na(B.Orb))

# Filter out fails, positive and negative controls
qpcr_good <- qpcr %>%
  filter(!(is.na(C.Orb) & is.na(D.Orb) & is.na(A.Orb) & is.na(B.Orb))) %>%
  filter(Sample.Name != "PTC") %>%
  filter(Sample.Name != "NTC")

# Convert ratios that are NaN to zero
qpcr_good <- qpcr_good %>%
  mutate(A.Orb = ifelse(is.na(A.Orb), 0, A.Orb),
         B.Orb = ifelse(is.na(B.Orb), 0, B.Orb),
         C.Orb = ifelse(is.na(C.Orb), 0, C.Orb),
         D.Orb = ifelse(is.na(D.Orb), 0, D.Orb))


# Assigning dominant Symbiodiniaceae based on ratio
qpcr_good <- qpcr_good %>%
  mutate(dom_sym = case_when(B.Orb > C.Orb & B.Orb > D.Orb & B.Orb > A.Orb ~ "Breviolum",
                             C.Orb > B.Orb & C.Orb > D.Orb & C.Orb > A.Orb ~ "Cladocopium",
                             D.Orb > B.Orb & D.Orb > C.Orb & D.Orb > A.Orb ~ "Durusdinium",
                             A.Orb > B.Orb & A.Orb > C.Orb & A.Orb > D.Orb ~ "Symbiodinium")) %>%
  mutate(dom_sym = factor(dom_sym))
```

#Filtering out replicated samples 
```{r}
#Determing which samples have been replicated in the data set
dupes <- qpcr_good %>%
  dplyr::count(Sample.Name) %>%
  filter(n > 1)

#Gathering the full data for replicated samples
qpcr_dupes <- qpcr_good %>%
  filter(Sample.Name %in% dupes$Sample.Name) %>%
  arrange(Sample.Name)

#Filtering out replicated samples with only 1 technical replicate for a symbiont
qpcr_dupes_f1 <- qpcr_dupes %>%
  group_by(Sample.Name) %>%
  filter(A.reps != 1, B.reps != 1, C.reps != 1, D.reps != 1) %>%
  ungroup()

#Calculating average standard deviation per sample and selecting lower average SD
qpcr_dupes_f2 <- qpcr_dupes_f1 %>%
  rowwise() %>%
  mutate(avg_sd = mean(c(A.CT.sd, B.CT.sd, C.CT.sd, D.CT.sd), na.rm = TRUE)) %>%
  group_by(Sample.Name) %>%
  filter(avg_sd == avg_sd[which.min(avg_sd)])

qpcr_good <- qpcr_good %>%
  filter(!Sample.Name %in% dupes$Sample.Name) %>%
  bind_rows(qpcr_dupes_f2)
  

setdiff(qpcr_dupes$Sample.Name, qpcr_dupes_f2$Sample.Name)


setdiff(qpcr$Sample.Name, qpcr_good$Sample.Name)
```

#Import depth data and add to qpcr_good df
```{r}
#library(readr)

#Importing field sample collection data 
sample_data <- readxl::read_xlsx("Data/Temperature/sample_data.xlsx")

sample_collect <- sample_data %>%
  select(Sample.Name = tube_label, depth = colony_depth_m, site)

# Each sample name and associated depth 
depth <- sample_collect %>%
  select(Sample.Name, depth)

#Table of Site Depth Metrics
metrics <- sample_collect %>%
  group_by(site) %>%
  summarize(
    mean = mean(depth, na.rm = TRUE),
    min = min(depth, na.rm = TRUE),
    max = max(depth, na.rm = TRUE),
    median = median(depth, na.rm = TRUE))
```

  



#Figure 4. Host genotype diversity and Symbiodiniaceae composition of colonies from Mermaid Reef and Sandy Cay. 
```{r}
# Host genotypes data table 
table_genotypes <- tibble(
  colony = c(rep(1:12, 2)),
  reef = c(rep("Mermaid Reef", 12), rep("Sandy Cay Reef", 12)),
  genotype = c(rep("a", 12), "b", "c", "d", "e", "f", "g", "h", "i",
               "j", "k", rep("l", 2)))

# Host genotypes separated by site  
plot_genotypes <- ggplot(data = table_genotypes,mapping = aes(x = colony, fill = genotype)) +
  geom_bar(position = "fill") +
  scale_x_discrete(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  scale_fill_manual(values = c('#fdb462','#8dd3c7','#ffffb3','#bebada','#fb8072','#80b1d3','#b3de69','#fccde5','#d9d9d9','#bc80bd','#ccebc5','#ffed6f')) +
  labs(x = "", y = "Host Genotype") +
  theme_classic() +
  facet_wrap(~ reef) +
  theme(legend.position = "none", axis.title = element_text(size = 8),
        strip.text = element_text(size = 8),
        axis.text.y = element_text(color = "transparent"),
        axis.ticks.y = element_blank())

# Change Symbiodiniaceae from clade name to genus, Add in "site" column  
sym_commun <- qpcr_good %>%
  select(Sample.Name, A.Orb, B.Orb, C.Orb, D.Orb) %>%
  mutate(Symbiodinium = case_when(A.Orb > 0 ~ A.Orb),
         Breviolum = case_when(B.Orb > 0 ~ B.Orb),
         Cladocopium = case_when(C.Orb > 0 ~ C.Orb),
         Durusdinium = case_when(D.Orb > 0 ~ D.Orb)) %>%
  select(Sample.Name, Symbiodinium, Breviolum, Cladocopium, Durusdinium) %>%
  gather(key = "sym", value = "value", -Sample.Name) %>%
  mutate(site = factor(str_sub(Sample.Name, start = 1, end = 2))) 


# Composition of Symbiodiniaceae in each sample with associated depth 
sym_commun_depth <- sym_commun %>%
  right_join(depth) %>%
  mutate(value = ifelse(is.na(value), 0, value))%>%
  mutate(depth_int = cut(depth, breaks = 8)) %>%
  mutate(newcol = paste(depth, Sample.Name))
 
# Establishing label for sites 
sites <- as_labeller(c(SC = "Sandy Cay Reef", MR = "Mermaid Reef"))

# Symbiodiniaceae Composition by site 
symbiont_comp_f <- ggplot(sym_commun_depth, aes(x = newcol, y = value, fill = sym)) +
  geom_bar(stat = "identity", position = "fill") +
  facet_grid(~site, scales = "free", labeller = sites) +
  ylab("Symb. Proportions") +
  labs(fill = "") +
  theme_classic() +
  labs(x = "") +
  scale_fill_manual(values = c('#a6cee3','#1f78b4','#b2df8a','#33a02c')) +
  scale_x_discrete(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  theme(legend.position = "bottom", 
        legend.text = element_text(size = 8, face = "italic"),
        axis.title = element_text(size = 8),
        strip.text = element_text(size = 8),
        axis.text.x = element_text(size = 0, color = "transparent", margin = margin(t = -20)),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(),
        strip.background = element_blank(),
        strip.text.x = element_blank())



# Combined Host Genotype and Symbiodiniaceae composition figure separated by site (Figure 4)
cowplot::plot_grid(plot_genotypes, symbiont_comp_f, 
                   nrow = 2, rel_heights = c(0.9, 1),
                   labels = "auto")

ggsave(filename = "figures/Fig4.png", width = 174, height = 100, units = "mm")

```


#Figure 5. Proportion of colonies with the dominant Symbiodiniaceae genus at a given depth.
```{r}
#Restructure Symbiodiniaceae qpcr data frame from wide to long
qpcr_good_long <- qpcr_good %>%
  select(Sample.Name, A.Orb, B.Orb, C.Orb, D.Orb, dom_sym) %>%
  gather(key = "sym", value = "value", -Sample.Name, -dom_sym)

#Add depth of each sample to qpcr_good data frame, Adjust depth values to 2 decimal places 
depth_dom_sym <- sample_collect %>%
  right_join(qpcr_good_long) %>%
  distinct(Sample.Name, depth, dom_sym, site) %>%
  mutate(depth = case_when(site == "mermaid_reef" & depth == 2.6 ~ 2.59,
                           site == "sandy_cay" & depth == 2.6 ~ 2.61,
                           TRUE ~ depth))

#Summarise samples into depth ranges
grouped_depth <- depth_dom_sym %>%
  select(depth, dom_sym) %>%
  mutate(depth_int = cut(depth, breaks = c(1.1, seq(2.6, 7.6, 1.25)))) %>%
  mutate(depth_int = case_when(grepl("1.1,2.6", depth_int) ~ "1.10 - 2.60",
                               grepl("2.6,3.85", depth_int) ~ "2.60 - 3.85",
                               grepl("3.85,5.1", depth_int) ~ "3.85 - 5.10",
                               grepl("5.1,6.35", depth_int) ~ "5.10 - 6.35",
                               grepl("6.35,7.6", depth_int) ~ "6.35 - 7.60")) %>%
  group_by(depth_int, dom_sym) %>%
  summarise(ncol = n()) %>%
  mutate(n = sum(ncol), label = paste0("N =", n)) %>%
  mutate(prop = ncol/n)

#Plot proportion of dominant Symbiodiniaceae by depth interval (Figure 5)
ggplot(grouped_depth, aes(x = as.factor(depth_int), y = ncol, fill = dom_sym)) +
  geom_bar(stat = "identity", position = "fill") +
  geom_text(aes(x = as.factor(depth_int), y = 1.01, label = label), size = 1.5, inherit.aes = FALSE) +
  scale_fill_manual(values = c('#a6cee3','#1f78b4','#b2df8a','#33a02c')) + 
  geom_vline(xintercept = 1.5, lty = 2, lwd = 0.5) +
  xlab("Depth (m)") +
  ylab("Proportion  of colonies") +
  annotate("text", x = 1.68, y = 1.05, size = 2.1, label = "  Mermaid Reef    Sandy Cay Reef →") +
  scale_y_continuous(expand = c(0,0.02)) +
  theme_classic() +
  theme(axis.title = element_text(size = 8),
        axis.text = element_text(size = 5, color = "black"),
        legend.title = element_blank(),
        legend.text = element_text(face = "italic", size = 5),
        legend.spacing.x = unit(0.1, 'cm'),
        legend.position = "bottom",
        legend.key = element_rect(size = 0.3, linetype = "blank"))
        

ggsave(filename = "figures/Fig5.png", width = 84, height = 84, units = "mm")

```



# Figure 6. Network analysis of Symbiodiniaceae composition of Orbicella faveolata from a)Mermaid Reef and b)Sandy Cay Reef

# a) Mermaid Reef Network Figure 
```{r}
library(igraph) #install.packages("igraph")
library(fields) #install.packages("fields")

#proportion of each Symbiodiniaceae genus in each sample
net_data_MR <- qpcr_good %>%
  select(Sample.Name, A.Orb, B.Orb, C.Orb, D.Orb) %>%
  merge(depth_dom_sym) %>%
  filter(site == "mermaid_reef") %>%
  select(Sample.Name, D.Orb) %>%
  mutate(D.prop = D.Orb/D.Orb) %>%
  select(Sample.Name, D.prop)

# Edge List
edges_MR <- net_data_MR %>%
  gather(key = "Clade", value = "weight", -Sample.Name) %>%
  filter(weight != 0)

# Depth of each sample
depth_MR <- depth_dom_sym %>%
  select(Sample.Name, depth, site) %>%
  filter(site == "mermaid_reef") %>%
  select(Sample.Name, depth)

#Vertices List
verts_MR <- tibble(Sample.Name = c(net_data_MR$Sample.Name, colnames(net_data_MR)[-1])) %>%
  left_join(depth_MR) %>%
  rename(id = Sample.Name) %>%
  mutate(lab = case_when(grepl("SC", id) ~ "",
                         grepl(".prop", id) ~ str_sub(id, start = 1, end = 1)))

# Network Figure 
net_MR <- graph_from_data_frame(edges_MR, directed = FALSE, vertices = verts_MR)

png("Figures/MR_Network.png", width = 200, height = 200, units = "mm", res = 600)

set.seed(8)

plot(net_MR, edge.curved = 0, 
     edge.width = 10 * (E(net_MR)$weight)^0.5, 
     vertex.label = V(net_MR)$lab,
     vertex.label.font = 2,
     vertex.label.cex = 2.5,
     vertex.label.color = "black",
     vertex.size = ifelse(grepl("MR", names(V(net_MR))), 10, 30),
     vertex.color = ifelse(grepl("MR", names(V(net_MR))), 
                           colorRampPalette(c("gray94"))(100)[as.numeric(cut(V(net_MR)$depth,breaks = 100))],
                           c("#1f78b4")))

dev.off()

```

# b) Sandy Cay Reef Network Figure 
```{r}
# Proportion of each Symbiodiniaceae genus in each Sample
net_data_SC <- sample_collect %>%
  select(Sample.Name, site) %>%
  merge(qpcr_good, by = "Sample.Name") %>%
  select(Sample.Name, A.Orb, B.Orb, C.Orb, D.Orb, site) %>%
  filter(site == "sandy_cay") %>% 
  mutate(total = A.Orb + B.Orb + C.Orb + D.Orb, 
         A.prop = A.Orb/total,
         B.prop = B.Orb/total,
         C.prop = C.Orb/total,
         D.prop = D.Orb/total) %>%
  select(Sample.Name, Symbiodinium = A.prop, Breviolum = B.prop, Cladocopium = C.prop, Durisdinium = D.prop)

# Edge List 
edges_SC <- net_data_SC %>%
  gather(key = "Genera", value = "weight", -Sample.Name) %>%
  filter(weight != 0)

# Depth of Each Sample
depth_SC <- depth_dom_sym %>%
  select(Sample.Name, depth, site) %>%
  filter(site == "sandy_cay") %>%
  select(Sample.Name, depth) 

# Verts_List
verts_SC <- tibble(Sample.Name = c(net_data_SC$Sample.Name, colnames(net_data_SC)[-1])) %>%
  left_join(depth_SC) %>%
  rename(id = Sample.Name) %>%
  mutate(lab = case_when(grepl("SC", id) ~ "", grepl("um", id) ~ str_sub(id, start = 1, end = 1))) 
 
# Network Figure 
net_SC <- graph_from_data_frame(edges_SC, directed = FALSE, vertices = verts_SC)

png("Figures/SC_Network.png", width = 200, height = 200, units = "mm", res = 600)

set.seed(40) #57, 63, 66, 85

plot(net_SC, edge.curved = 0, 
     edge.width = 15 * (E(net_SC)$weight)^0.5, 
     edge.color = "gray65",
     vertex.label = V(net_SC)$lab,
     vertex.label.font = 2,
     vertex.label.cex = 2.5,
     vertex.label.color = "black", 
     vertex.size = ifelse(grepl("SC", names(V(net_SC))), 10, 25),
     vertex.color = ifelse(grepl("SC", names(V(net_SC))), 
                           colorRampPalette(c("white", "black"))(100)[as.numeric(cut(V(net_SC)$depth,breaks = 100))],
                           c('#a6cee3','#1f78b4','#b2df8a','#33a02c')))

image.plot(legend.only = TRUE, 
           zlim = range(V(net_SC)$depth, na.rm = TRUE),
           horizontal = TRUE,
           legend.shrink = 0.6,
           legend.lab = "Depth (m)",
           col = colorRampPalette(c("white", "black"))(100))


dev.off()

```


